A catalog of wide binaries and comoving star pairs from \textsl{Gaia DR1} and low-resolution spectroscopy

### 2017-07-05 paper/comoving-followup.tex
change section name
adjust figure sizes
one more todo on contamination rate

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{wavelength_gp.pdf}
  \end{center}
  \caption{%
    A visualization of the pixel-to-wavelength model determined from a single
    wavelength comparison lamp spectrum.
    Black markers show the fit pixel centroids for known Hg or Ne emission
    lines and the residual wavelength value between the linear + GP model and
    the true emission line centroid.
    The non-shaded region shows the section of spectrum where the comparison
    lamp spectrum has sufficient line density to determine the wavelength
    solution; shaded regions are masked from the resulting spectra.
    Orange envelope shows the root-variance of the Gaussian process component
    of the model, which can be interpreted as inherent uncertainties on the
    wavelength calibration as a result of the model flexibility.
    \label{fig:wavelength-GP}}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{sample_spectra.pdf}
  \end{center}
  \caption{%
    A section of 10 randomly selected target spectra from this work.
    Spectral fluxes are normalized to 1 at $\lambda = 5500~{\rm \AA}$ and the
    offsets are chosen to separate the spectra for visualization.
    The spectra are smoothed with a Gaussian filter with root-variance $\sigma
    = 2~{\rm \AA}$.
    \label{fig:sample-spectra}}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{llr-vs-dv.pdf}
  \end{center}
  \caption{%
    FML
    \label{fig:llr}}
\end{figure}

@@

At separations $\gtrsim 1~\pc$, $\approx 40\%$ of the comoving pairs are
genuinely comoving; interestingly, the separation distribution of the genuine
pairs appears to be at least uniform or possibly growing in number as the
separation increases.
This strongly suggests the existence of a population of unbound wide binaries or
dissolved open clusters, which maintain approximate spatial coherence for long
times because of the small relative velocities at the time of disruption of the
constituent stars (e.g., \citealt{Jiang:2010}).
The kinematic properties of these unbound binaries and associations contain
information about the tidal field and fluctuations in the mass distribution of
the Milky Way.
With \gaia\ \DR{2}, we will be able to study the statistical properties of these
widely-separated but comoving stars at even larger separations ($>10~\pc$).

@@

\subsection{Interesting comoving pairs}\label{sec:interesting-pairs}

>>>>

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.8\linewidth]{wavelength_gp.pdf}
  \end{center}
  \caption{%
    A visualization of the pixel-to-wavelength model determined from a single
    wavelength comparison lamp spectrum.
    Black markers show the fit pixel centroids for known Hg or Ne emission
    lines and the residual wavelength value between the linear + GP model and
    the true emission line centroid.
    The non-shaded region shows the section of spectrum where the comparison
    lamp spectrum has sufficient line density to determine the wavelength
    solution; shaded regions are masked from the resulting spectra.
    Orange envelope shows the root-variance of the Gaussian process component
    of the model, which can be interpreted as inherent uncertainties on the
    wavelength calibration as a result of the model flexibility.
    \label{fig:wavelength-GP}}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.6\linewidth]{sample_spectra.pdf}
  \end{center}
  \caption{%
    A section of 10 randomly selected target spectra from this work.
    Spectral fluxes are normalized to 1 at $\lambda = 5500~{\rm \AA}$ and the
    offsets are chosen to separate the spectra for visualization.
    The spectra are smoothed with a Gaussian filter with root-variance $\sigma
    = 2~{\rm \AA}$.
    \label{fig:sample-spectra}}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.7\linewidth]{llr-vs-dv.pdf}
  \end{center}
  \caption{%
    FML
    \label{fig:llr}}
\end{figure}

@@

\todo{Discuss contamination rate vs. separation for ratio cut of 6?}
At separations $\gtrsim 1~\pc$, $\approx 40\%$ of the comoving pairs are
genuinely comoving; interestingly, the separation distribution of the genuine
pairs appears to be at least uniform or possibly growing in number as the
separation increases.
This strongly suggests the existence of a population of unbound wide binaries or
dissolved open clusters, which maintain approximate spatial coherence for long
times because of the small relative velocities at the time of disruption of the
constituent stars (e.g., \citealt{Jiang:2010}).
The kinematic properties of these unbound binaries and associations contain
information about the tidal field and fluctuations in the mass distribution of
the Milky Way.
With \gaia\ \DR{2}, we will be able to study the statistical properties of these
widely-separated but comoving stars at even larger separations ($>10~\pc$).

@@

\subsection{Highlighted comoving pairs}\label{sec:interesting-pairs}
